```{r echo = FALSE}
knitr::opts_chunk$set(out.width = "100%")
```

# Using programming platforms on AnVIL

Modules about opening, touring, and closing AnVIL platforms

<br>

## Video overview on using Jupyter Notebooks 

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_jupyter_video.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Launching Jupyter

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_jupyter_launch.Rmd",
  branch = "jupyter-launch-add-workspace-name",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Video overview on using Galaxy

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_galaxy_video.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Starting Galaxy

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_galaxy_start.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Navigating Galaxy

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_galaxy_navigate.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Deleting Galaxy

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_galaxy_delete.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Video overview on using RStudio

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_rstudio_video.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Launching RStudio

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_rstudio_launch.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Touring RStudio

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_rstudio_tour.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Pausing RStudio

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_rstudio_pause.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Deleting RStudio

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_rstudio_delete.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Pausing vs. Deleting cloud environments

These instructions can be customized by setting the following variables in `AnVIL_module_settings` before running `cow::borrow_chapter()`:

- `cloud_environment`: (string) specify the type of cloud environment. Defaults to "your cloud environment"
- `include_pd_details`: (bool) whether to include an explanation about keeping the Persistent Disk. Defaults to FALSE

### Generic cloud environment, with PD details

```
AnVIL_module_settings <- list(include_pd_details = TRUE)
cow::borrow_chapter(
  doc_path = "child/_child_cloud_environment_pause_vs_delete.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
AnVIL_module_settings <- list(include_pd_details = TRUE)
cow::borrow_chapter(
  doc_path = "child/_child_cloud_environment_pause_vs_delete.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

### RStudio, with no PD details

```
AnVIL_module_settings <- list(cloud_environment = "RStudio")
cow::borrow_chapter(
  doc_path = "child/_child_cloud_environment_pause_vs_delete.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
AnVIL_module_settings <- list(cloud_environment = "RStudio")

cow::borrow_chapter(
  doc_path = "child/_child_cloud_environment_pause_vs_delete.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

