# Why use AnVIL?

The NHGRI AnVIL (Genomic Data Science Analysis, Visualization, and Informatics Lab-space) is a project powered by Terra for biomedical researchers to access data, run analysis tools, and collaborate. Both biology researchers and educators can benefit from using AnVIL [(anvil.terra.bio)](anvil.terra.bio) for their research and in the classroom. This guide acts as a resource answering the question "why use AnVIL?".

## Benefits of using AnVIL for research

### User-friendly process of accessing and interacting with the AnVIL platform

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
    doc_path = "child/_child_why_anvil_research_platformAccess.Rmd",
    repo_name = "jhudsl/AnVIL_Template",
    remove_h1 = TRUE,
    branch = "why_anvil"
)
```

### Variety of available analysis solutions/frameworks and tools

```{r echo=FALSE, out.width = "100%", fig.alt = ""}
ottrpal::include_slide("https://docs.google.com/presentation/d/1zq27o5gSWeiaEPqbCTTL3c_zvozN5lg_QNJYRVyM-SI/edit?slide=id.g36e681c6048_0_142#slide=id.g36e681c6048_0_142")
```

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
    doc_path = "child/_child_why_anvil_research_platformInteroperability.Rmd",
    repo_name = "jhudsl/AnVIL_Template",
    remove_h1 = TRUE,
    branch = "why_anvil"
)
```

### Ability to bring your own data or (with proper permissions) work with controlled access data

```{r echo=FALSE, out.width = "100%", fig.alt = ""}
ottrpal::include_slide("https://docs.google.com/presentation/d/1zq27o5gSWeiaEPqbCTTL3c_zvozN5lg_QNJYRVyM-SI/edit?slide=id.g36e681c6048_0_91#slide=id.g36e681c6048_0_91")
```

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
    doc_path = "child/_child_why_anvil_research_data.Rmd",
    repo_name = "jhudsl/AnVIL_Template",
    remove_h1 = TRUE,
    branch = "why_anvil"
)
```

### Data and analysis methods in one place

```{r echo = FALSE, out.width = "100%", fig.alt = ""}
ottrpal::include_slide("https://docs.google.com/presentation/d/1zq27o5gSWeiaEPqbCTTL3c_zvozN5lg_QNJYRVyM-SI/edit?slide=id.g36e681c6048_0_179#slide=id.g36e681c6048_0_179")
```

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
    doc_path = "child/_child_why_anvil_research_inverted.Rmd",
    repo_name = "jhudsl/AnVIL_Template",
    remove_h1 = TRUE,
    branch = "why_anvil"
)
```

### Scalability and flexibility in use

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
    doc_path = "child/_child_why_anvil_research_scale.Rmd",
    repo_name = "jhudsl/AnVIL_Template",
    remove_h1 = TRUE,
    branch = "why_anvil"
)
```

### Maintenance and upkeep of hardware and software are handled by AnVIL -- you just rent what you need

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
    doc_path = "child/_child_why_anvil_research_maintenance.Rmd",
    repo_name = "jhudsl/AnVIL_Template",
    remove_h1 = TRUE,
    branch = "why_anvil"
)
```

### Group and workspace management structure for role-based permissions and collaboration

```{r echo = FALSE, out.width = "100%", fig.alt = ""}
ottrpal::include_slide("https://docs.google.com/presentation/d/1zq27o5gSWeiaEPqbCTTL3c_zvozN5lg_QNJYRVyM-SI/edit?slide=id.g36e681c6048_0_152#slide=id.g36e681c6048_0_152")
```

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
    doc_path = "child/_child_why_anvil_research_workspaceRole.Rmd",
    repo_name = "jhudsl/AnVIL_Template",
    remove_h1 = TRUE,
    branch = "why_anvil"
)
```

### Create, share, and reuse reproducible analysis workspaces

```{r echo = FALSE, out.width = "100%", fig.alt = ""}
ottrpal::include_slide("https://docs.google.com/presentation/d/1zq27o5gSWeiaEPqbCTTL3c_zvozN5lg_QNJYRVyM-SI/edit?slide=id.g36e681c6048_0_166#slide=id.g36e681c6048_0_166")
```

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
    doc_path = "child/_child_why_anvil_research_workspaceShare.Rmd",
    repo_name = "jhudsl/AnVIL_Template",
    remove_h1 = TRUE,
    branch = "why_anvil"
)
```

## Benefits of using AnVIL in the classroom

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
    doc_path = "child/_child_why_anvil_classroom.Rmd",
    repo_name = "jhudsl/AnVIL_Template",
    remove_h1 = TRUE,
    branch = "why_anvil"
)
```

```{r, echo = FALSE, out.width = "100%", fig.alt = ""}
ottrpal::include_slide("https://docs.google.com/presentation/d/1zq27o5gSWeiaEPqbCTTL3c_zvozN5lg_QNJYRVyM-SI/edit?slide=id.g36e681c6048_0_34#slide=id.g36e681c6048_0_34")
```

## Overall benefits of AnVIL

### Ability to control costs

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
    doc_path = "child/_child_why_anvil_general_costControl.Rmd",
    repo_name = "jhudsl/AnVIL_Template",
    remove_h1 = TRUE,
    branch = "why_anvil"
)
```

### Work with protected data safely on AnVIL

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
    doc_path = "child/_child_why_anvil_general_protectedData.Rmd",
    repo_name = "jhudsl/AnVIL_Template",
    remove_h1 = TRUE,
    branch = "why_anvil"
)
```

### Focus on your work, not on maintaining the platform

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
    doc_path = "child/_child_why_anvil_general_maintenance.Rmd",
    repo_name = "jhudsl/AnVIL_Template",
    remove_h1 = TRUE,
    branch = "why_anvil"
)
```

### Training and support is available for users

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
    doc_path = "child/_child_why_anvil_general_support.Rmd",
    repo_name = "jhudsl/AnVIL_Template",
    remove_h1 = TRUE,
    branch = "why_anvil"
)
```

```{r echo=FALSE, out.width = "100%", fig.alt = ""}
ottrpal::include_slide("https://docs.google.com/presentation/d/1zq27o5gSWeiaEPqbCTTL3c_zvozN5lg_QNJYRVyM-SI/edit?slide=id.g36e681c6048_0_185#slide=id.g36e681c6048_0_185")
```

### AnVIL is a collaborative community with a development mindset

```{r echo=FALSE, out.width="100%", fig.alt = ""}
ottrpal::include_slide("https://docs.google.com/presentation/d/1zq27o5gSWeiaEPqbCTTL3c_zvozN5lg_QNJYRVyM-SI/edit?slide=id.g36e681c6048_0_147#slide=id.g36e681c6048_0_147")
```

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
    doc_path = "child/_child_why_anvil_general_community.Rmd",
    repo_name = "jhudsl/AnVIL_Template",
    remove_h1 = TRUE,
    branch = "why_anvil"
)
```

All of this together describes how the AnVIL provides secure, cost-effective genomic analysis at scale.

```{r echo = FALSE, out.width = "100%", fig.alt = ""}
ottrpal::include_slide("https://docs.google.com/presentation/d/1zq27o5gSWeiaEPqbCTTL3c_zvozN5lg_QNJYRVyM-SI/edit?slide=id.p#slide=id.p")
```
